Self Referencing Sequences

### 2014-11-06 draft.tex
Typo fix

\begin{corollary}
If two self-referencing sequences are generated over the same cycle and  then the read distance of their shared subsequence is the same everywhere.
\end{corollary}

@@

It is unclear to us whether all sequences generated by the same cycle are equivalent. This is certainly the case for $C=(123)$ and any two element cycles but we have been unable to generalize this to other three element or larger cycles. A key ingredient in establishing a counterexample would be more stringent necessary conditions for equivalence but it is unclear what these conditions should be or how to prove they are necessary. In order to establish that all sequences generated by the same cycle are in fact equivalent we would like to establish weaker or more generalizable sufficient conditions for equivalence, but based on our proof of Theorem ~\ref{eqsuff} it does not seem like weaker conditions will actually be sufficient.

>>>>

\begin{corollary}
If two self-referencing sequences are generated over the same cycle  and are equivalent then the read distance of their shared subsequence is the same everywhere.
\end{corollary}

@@

It is unclear to us whether all sequences generated by the same cycle are equivalent. This is certainly the case for $C=(123)$ and any two element cycles but we have been unable to generalize this to other three element or larger cycles. A key ingredient in establishing a counterexample would be more stringent necessary conditions for equivalence but it is unclear what these conditions should be or how to prove they are necessary. In order to establish that all sequences generated by the same cycle are in fact equivalent we would like to establish weaker or more generalizable sufficient conditions for equivalence, but based on our proof of Theorem ~\ref{equivsuff} it does not seem like weaker conditions will actually be sufficient.
